The Ky Fan Norms and Beyond: Dual Norms and Combinations for Matrix Optimization

### 2025-12-01 article_final/main.tex
rearranged the figures a little bit

\begin{figure}[htbp]
\floatconts
  {fig:app_lls}
  {\caption{More plots for linear least squares problem for a 500x500 matrix.}}
  {%
    \subfigure[The spectral norm of the gradient]{\label{fig:lls_op_grad_norm}%
      \includegraphics[width=0.5\linewidth]{figs/simple_lls/gradient_spectral_norm_vs_iteration_long_run.pdf}}%
    \vspace{1em}
    \subfigure[The nuclear norm of the gradient]{\label{fig:lls_nuclear_grad_norm}%
      \includegraphics[width=0.5\linewidth]{figs/simple_lls/gradient_nuclear_norm_vs_iteration_long_run.pdf}}%
    \vspace{1em}
    \subfigure[The loss over time]{\label{fig:lls_loss_time}%
      \includegraphics[width=0.5\linewidth]{figs/simple_lls/loss_vs_time_long_run.pdf}}
  }
\end{figure}

>>>>

\begin{figure}[htbp]
\floatconts
  {fig:app_lls}
  {\caption{More plots for linear least squares problem for a 500x500 matrix.}}
  {%
    \subfigure[The spectral norm of the gradient]{\label{fig:lls_op_grad_norm}%
      \includegraphics[width=0.49\linewidth]{figs/simple_lls/gradient_spectral_norm_vs_iteration_long_run.pdf}}%
    \hfill
    \subfigure[The nuclear norm of the gradient]{\label{fig:lls_nuclear_grad_norm}%
      \includegraphics[width=0.49\linewidth]{figs/simple_lls/gradient_nuclear_norm_vs_iteration_long_run.pdf}}%
    \vspace{1em}
    \subfigure[The loss over time]{\label{fig:lls_loss_time}%
      \includegraphics[width=0.49\linewidth]{figs/simple_lls/loss_vs_time_long_run.pdf}}
  }
\end{figure}
